\chapter{Abstract} \label{ch:Abstract}

This project is the Bachelor thesis for two students in electronic engineering at Aarhus University School of Engineering (ASE). The project addresses an automatic watering system comprised of a sensor and a control box, and is intended for Individuals with an interest in gardening. The system works by placing the sensor in the soil that needs watering. The sensor measures the surface temperature, soil humidity, and light intensity. The data is then transmitted via wireless communication to the control box, which maintains the chosen soil humidity by opening and closing an internal valve. The user connects the control box to the tap via a garden hose and the other end to an optional water dispenser. The use has the opportunity to select the level of soil humidity to be maintained, and if the system should water either morning, evening or the whole day.  \newline

The product is developed from scratch and throughout the development process several PCB’s for the sensor and controlbox were manufactured. One of the main issue for the project has been to develop a method for measuring soil humidity. At first, a resistive-measurement method was tested which came out quite imprecise. Next a capacitive-measurement method was tested, this method was shown to have great measurement characteristics but a great challenge was faced designing a	properly functioning and stable circuit to measure the variable capacitance.  Lastly, due to lack of time a rather simple capacitance-measurement circuit was implemented, this was shown to be sensitive to variation in temperature. Another main issue for the project was to design and implement a technical solution for wirelessly transmitting the data from sensor to controlbox. This was achieved by an 433MHz Transceiver, furthermore this was specially design for battery-applications. At the date of closure for the project, an almost fully functional prototype is ready. Only a few, less significant functionalities await implementation in this 1st. iteration.

\newpage